
1.	**Exploration:** \
We recognize the importance of space exploration for the future of humanity, both in terms of scientific discovery and potential resources.
Therefore, we will actively explore and chart the vast expanse of space, seeking out new worlds and discovering the mysteries of the universe.


2.	**Cooperation:** \
We will work together as a global community, pooling our resources and knowledge to achieve common goals.

3.	**Sustainability:** \
We will use sustainable and environmentally friendly technologies to minimize our impact on the cosmos.

4.	**Innovation:** \
We will push the boundaries of science and technology, developing new and revolutionary ways to travel, live, and thrive in space.

5.	**Education:** \
We will educate future generations about the wonders of space and inspire them to take part in humanity's journey into the stars.

6.	**Peace:** \
We will use our shared passion for space exploration to bring people together and promote peace and understanding between nations and cultures.

7.	**Survival:** \
We will ensure the survival and prosperity of our species by establishing permanent settlements on other planets, as a hedge against the eventual extinction of humanity on Earth.

8.	**Ethics:** \
We will respect the potential for other forms of intelligent life, and consider the ethical implications of our actions in space.

9.	**Openness:** \
We will promote open access to the data and knowledge gained through space exploration and encourage the participation of people from all backgrounds.

10.	**Progress:** \
We will strive to make steady progress in our understanding and mastery of space, while being mindful of the potential risks and benefits of our actions.
